---
title: "Clena, a tool for differentially expressed genes cluster-pathway enrichment analysis and visualization"
author: "Zhilong Jia"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

Pathway analysis plays an essential role in understanding the underlying biological mechanism of differentially expressed genes and proteins from a high-level view with a reduced complexity. Inversely, however, it probably overlooks some significant genes concerning the biological or clinic states.  To solve this problem, we developed a freely available R/Bioconductor package, called  cluster-pathway enrichment analysis (clena), for clustering the differentially expressed genes and analysing the pathway enrichment for clusters. Clena could apply a variety of clustering methods, such as hierarchical cluster and self-organising mapping, to the expression profiling of differentially expressed genes based on various distance metrics. After obtaining the clusters, clena could make pathway enrichment analysis as well as its visualization. These pathways can be gene sets from the Molecular Signatures Database (MSigDB) or even user-defined gene sets. By analysing the pathway enrichment of clusters, we could get more detailed biological explanation with each cluster so as to discovering some key clusters and genes relevant to the biological states. To illustrate the application of clena, we use a Parkinson's Disease dataset as an example. 

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` setion of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
